---
title: "Data 607 Week 3 Assignment"
author: "Yohannes Deboch"
date: "February 16, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Copy the introductory example. The vector name stores the extracted names.
```{r}
library(stringr)

```
```{r}
raw.data<-"555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"
raw.data
```

(a) Use the tools of this chapter to rearrange the vector so that all elements conform to
the standard first_name last_name .
```{r}
name <- unlist(str_extract_all(raw.data,"[[:alpha:]., ]{2,}"))
name
```
```{r}
# Remove the title
name <- str_replace(name,"[[:alpha:]]{2,}\\. ", "")
name
```
```{r}
# Extract the first name
first_name <- str_extract(name, "^[[:alpha:]]+\\.?")
last_name <- str_extract(name, "[[:alpha:]]+$")
# Trim whitespace
first_name <- str_trim(first_name)
last_name <- str_trim(last_name)
first_last <-  str_c(first_name, last_name, sep = " ")
first_last
```

(b) Construct a logical vector indicating whether a character has a title (i.e., Rev. and
Dr. ).
(c) Construct a logical vector indicating whether a character has a second name.



4. Describe the types of strings that conform to the following regular expressions and
construct an example that is matched by the regular expression.
(a) [0-9]+\\$
Answer:
Match any number 0 to 9 one or more times followed by a $ charcter at the end.

```{r}
str <- "I've 1500$ for my monthly expenses."
str_extract(str,"[0-9]+\\$")
```

(b) \\b[a-z]{1,4}\\b
Answer: Matches any 1 to 4 charcter lowercase letter a to z in a whole word search.
```{r}
str <- "Any character one to four digit lowercase letter.No digits 123etc are allowed."
str_extract(str,"\\b[a-z]{1,4}\\b")
```

(c) .*?\\.txt$
Answer: This regular expression matches any character followed by ".txt" at then end.

```{r}
str <- c(".txt","file.txt","big_data.txt","I'm a word")
unlist(str_extract_all(str,".*?\\.txt$"))
```


(d) \\d{2}/\\d{2}/\\d{4}
Answer: This regular expression matches dates where the first and second part is 2 digit number and the last part is a 4 digit number.
```{r}
str_extract("02/16/2019","\\d{2}/\\d{2}/\\d{4}")
```

(e) <(.+?)>.+?</\\1>
Answer: This expressoin matches any html opening and closing tags.
```{r}
str_extract("<title>This is a title</title>","<(.+?)>.+?</\\1>")

```
9. The following code hides a secret message. Crack it with R and regular expressions.
Hint: Some of the characters are more revealing than others! The code snippet is also
available in the materials at www.r-datacollection.com.
```{r}
str <- "clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0Tanwo
Uwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigO
d6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5
fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr"

# Extract all the upper case
message <- unlist(str_extract_all(str,"[[:upper:].! ]"))
message
# Make a sentence by joining
message <- paste(message, collapse = "")
message
# Replace . by space
message <- str_replace_all(message,"\\."," ")
message
```

